### 2021-11-04 Final Doc/Chapters/Chapter5.tex
Added group cont. table

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1} 
This chapter will focus on the personal reflections held about this project at its' completion. This process is conducted by answering several questions about the project.
\\\\
\indent \textit{What did you learn while completing this project? Refer to the decisions that you took, and evaluate them. Analyse the strong and weak points of the product and the process that you followed. What would you do differently?}
\\
learn stuff
\\\\
\indent \textit{Did you achieve the objectives that you set for the project? Discuss.}
\\
list original goals and discuss
\\\\
\indent \textit{How successful were you in managing the project and meeting target dates? Discuss.}
\\
While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking. The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation were only completed a few days prior to the deadlines with final checks typically happing on the day of submission. 
\\\\
\indent \textit{Comments on group work. Responsibilities and contribution of each group member. Problems with cooperation and contributions, and dealing with these problems.}
\\
As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
\begin{itemize}
\item Joshua Esterhuizen was responsible for:
\begin{itemize}
\item a
\item b
\end{itemize}

\item GC Wehemeyer was responsible for:
\begin{itemize}
\item c
\item d
\end{itemize}

\item Rickus Trollip was responsible for:
\begin{itemize}
\item e
\item f
\end{itemize}
\end{itemize}

>>>>

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1} 
This chapter will focus on the personal reflections held about this project at its' completion. This process is conducted by answering several questions about the project.
\\\\
\indent \textit{What did you learn while completing this project? Refer to the decisions that you took, and evaluate them. Analyse the strong and weak points of the product and the process that you followed. What would you do differently?}
\\
learn stuff
\\\\
\indent \textit{Did you achieve the objectives that you set for the project? Discuss.}
\\
list original goals and discuss
\\\\
\indent \textit{How successful were you in managing the project and meeting target dates? Discuss.}
\\
While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking. The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation were only completed a few days prior to the deadlines with final checks typically happing on the day of submission. 
\\\\
\indent \textit{Comments on group work. Responsibilities and contribution of each group member. Problems with cooperation and contributions, and dealing with these problems.}
\\
As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
\begin{table}[H]
\begin{tabular}{l|l|l}
\hline
Joshua Esterhuizen       & GC Wehmeyer          & Rickus Trollip           \\ \hline
Player Movement          & Player Animation     & Main Menu                \\
Ball physics             & Health Bar           & Enemy AI                 \\
Moving platforms         & Player Model         & Game music aquisition    \\
Portal asset development & Enemy Models         & Controller configuration \\
Teleportation            & Environment assets   & Second Level designer    \\
Pause Menu               & Third Level designer &                          \\
Level Transition         &                      &                          \\
Tutorial level designer  &                      &                          \\ \hline
\end{tabular}
\end{table}
